---
title: "Using `captionr` to create caption labels"
author: "Jonathan Chung"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---
    ```{r, echo = FALSE}
    library(mdcaptionr)
    markers <- marker_obj()
    
    ```

# Creating a marker object and adding new markers

The caption markers are contained in a `marker_obj` which is a named list of
class `marker_obj`.

```{r, initialize_marker_object}
library(mdcaptionr)

# Initialize new marker object
markers <- marker_obj()
markers
```

To add a new marker, use the `label()` function. The `label` function checks 

```{r, add_label}
markers <- label(markers, "fig.awesome_figure")
markers
```

# Using `mdcaptionr`

## Setting up

At the begining of the document.

    ```{r, setup}
    library(mdcaptionr)
    markers <- marker_obj()
    ```

At the begining of each section, you need to add an R code block with the marker labels you will call in the section. This means that while writing, you need to go back to the begining of that section and add label markers after the fact.

### Awesome section
```{r, section_captions}
markers <- label(markers, "fig.awesome_figure")
```

```{r, echo=FALSE, fig.cap=print_caption(markers, "fig.awesome_figure", "Figure", "This is an awesome figure!")}
plot(cars)
```
